### 2015-10-13 weeklyReport/motivating.tex
init 10-12

\section{Motivating Example}

Consider that user wants to add undo and redo actions for their Java Swing text editor application with undo/redo buttons.  Without knowing any APIs, developer  first queries our tool with a free-form query \codefont{`java undo redo example'}. Our tool investigates top 10 web pages returned from Google, because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}. Our tool uses `expert' heuristic to filter and rank web pages: it favors pages that have complete code snippet and text description because these pages are more likely to be written by experts. Thus it removes 3 pages without explicit code snippets, and performs the initial parsing for the informal documentations to identify code-like terms.

\noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example. Based on a relative match threshold to measure the relative occurrence of the number of matched facts out of all class-level facts,  our tool clusters these examples in three groups using complete linkage technique: 5 examples use classes in Java Swing like `AbstractAction' and `UndoableEditListener', another example uses a `Node' data structure to illustrate how to implement undo/redo actions using command design pattern, and the last example is the javadoc for `UndoManager'.  Our tool starts from the first cluster as it has the highest relative occurrence out of all examples. Based on partial program analysis, we generate a list of type facts to infer types and bind methods.

@@

\input{example}

@@

\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.  If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples. Our tool asks for user's selection by presenting the generated main facts and related facts to the user in the form of code snippet. 
After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E.

>>>>

%\section{Motivating Example}

\begin{comment}
\noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example. Based on a relative match threshold to measure the relative occurrence of the number of matched facts out of all class-level facts,  our tool clusters these examples in three groups using complete linkage technique: 5 examples use classes in Java Swing like `AbstractAction' and `UndoableEditListener', another example uses a `Node' data structure to illustrate how to implement undo/redo actions using command design pattern, and the last example is the javadoc for `UndoManager'.  Our tool starts from the first cluster as it has the highest relative occurrence out of all examples. Based on partial program analysis, we generate a list of type facts to infer types and bind methods.

@@

@@

\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.  If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples. Our tool asks for user's selection by presenting the generated main facts and related facts to the user in the form of code snippet. 
After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E. 
\end{comment}

### 2015-10-13 weeklyReport/problem.tex
init 10-12

\section{Problem Statement}

Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.  In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.  During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.

@@

 \begin{figure*}[!htb]
    \centering
\includegraphics[width=1\textwidth]{fig/system.pdf}
       \caption{System process overview}
        \label{fig:system}
   \end{figure*}

>>>>

\section{Last week}

Based on our discussion last week, our problem statement includes:

\begin{enumerate}
\item Developers do not know the name of API elements a priori, though locating code example through existing search engine often expects the developers to know API elements' names.
\item Reuse tasks involve multiple related classes and methods, rather than a single method/class. Yet code search engines do not help developers recognize the latent structure among related classes/methods. (at the granularity of multiple methods)
\item During copy/paste based reuse, developers must remove irrelevant parts. Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts. (at the granularity of multiple examples)
\end{enumerate}

%We have three hypotheses correspondingly:
%\begin{enumerate}
%\item We believe that NLP text with partial code snippet could help us identify the name of API elements based on keywords from free-form query. 
%
%\item Our hypothesis is that we can find related elements by following the structural dependencies of seed API elements in code and by ranking other API elements potentially mentioned in natural language text. 
%
%\item We believe that clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts. 
%
%\end{enumerate}

I focus on the second and third problems, perform a preliminary study using three popular code search engines to illustrate these two problems, and revise the hypotheses based on our use of code search engine.

\section{Problem 2}
Problem: Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.

Hypothesis: We can find related elements by following the structural dependencies of seed API elements in code and by ranking these related API elements based on their topology structure.

Input: a free-form query that user provides to present her reuse intention.

Output: a list of classes/methods implementation that complete this reuse task.

Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?

To answer these two subquestions, I search for the evaluation dataset for existing code search tools using free-form query (SNIFF~\cite{sniff:Sen09}, Portfolio~\cite{Portfolio:DenysICSE11}, Sourcer~\cite{Sourcerer:SC14}, anyCode~\cite{Gvero:ICSE15}, and Keivanloo et al.~\cite{spotWork:ICSE14}), feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04},   and reuse tools~\cite{Holmes:reuse07, Holmes:ASE09}. Other code search engines such as Koders~\cite{Koders}, Krugle~\cite{Krugle}, and SearchCode~\cite{SearchCode} are available on the web, which can be used to assist programmers by providing relevant code examples with usages of the given free-form query from a large number of public source code repositories. Yet the results are sorted based on the text matching and they fail to recognize the latent structure among related classes/methods.

Based on Table~\ref{tab:concern} and Table~\ref{tab:reuse}, most medium-scale or large-scale reuse tasks involve multiple methods and classes.  However, existing code search tools and  feature location tools  do not help developers recognize the latent structure among related classes/methods. We do not focus on large-scale reuse task mentioned in~\cite{Holmes:reuse07, Holmes:ASE09}.

\input{eval-table}
\input{example}

In summary,  a feature/concern reuse task involves multiple related classes and methods. The developer should implement multiple methods and classes to finish the reuse task. Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code already exist. We argue that it requires multiple methods to implement a non-trivial feature/concern.

\section{Scenario}
\noindent{\textbf{Add undo and redo action for TextEditor.}}

\begin{table}[ht]
\begin{center}
\caption{Search Result from Code Search Engine}
\label{tab:total}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}c|llrr@{}} \hline
No.&Name&Project&LOC&\# M\\\hline
1&TextEditor&textmash&1270&12\\
2,3&AndroidTextEditor&android&576&9\\
4&DocumentUndoManagerImpl&ide&1227&17\\
5,6,8&ConsoleTextEditor&groovy&321&7\\ 
7&PapyrusCDTEditor&eclipse.papyrus&393&7\\
9,10&AspectEditorContributor&eclipse&88&2\\ \hline
\end{tabular*}
 \label{tab:undoResult}
 \textbf{ \# M} represents the number of methods that contain the query terms. 
 {\bf No.} represents the rank from CSE. Note that CSE may return the same results for multiple times, as the same file may exist in multiple branches. For instance, we regard 5,6,8 as identical with manual inspection.

}
 \end{center}
\end{table}

Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11}.  Consider that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons.  Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}. Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE. For each partial program returned from CSE, I select the top k (k=5) methods that are related to the given query.

%\subsection{Problem 3}
%Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.

%Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.

%We use the results for  the last three concerns implementation in Table~\ref{tab:concern} found by the code search engine SearchCode to illustrate the Problem 3.

\begin{comment}
Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.  In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.  During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.

@@

 \begin{figure*}[!htb]
    \centering
\includegraphics[width=1\textwidth]{fig/system.pdf}
       \caption{System process overview}
        \label{fig:system}
   \end{figure*}
\end{comment}
